Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-04-25 PaperVictor.tex
Ŕemove spaces inadvertently by Vivechna
Minor punctuation correction
Relabel figures
Relabel tables

\author[1]{V Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

@@

\begin{table}
        \centering
        \label{tab:tableA}
        \addtolength{\tabcolsep}{-2pt}
        \begin{tabular}{rrrrrrrrrr}
                Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
                \hline
                \hline
                $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
                $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
                $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
                \hline
                $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
                $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
                $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
        \end{tabular}
        \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
                reflectance $\braket{R}$ averaged over the spectral ranges
                $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
                the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
                $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
                of the structure and the omnidirectional spectral
                width and center (ODW and ODC).}
\end{table}

The function $f_{3}$ yields after optimization the highest
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
structure. Furthermore, this
structure has an omnidirectional width (ODW) of 250 nm
centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
photonic structures have been reported with
ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
which $R>90\%$ for all angles. Here we we adopt the same criterium.
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
        \label{Fig1}
        \begin{center}
                \includegraphics[width=\textwidth]{F1Alternativa.pdf}
        \end{center}
        \caption{Profiles of the functions $f_n(\xi_j)$ optimized for
                the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
                $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
                for non-polarized light
                vs. wavelength and angle of incidence of the structure
                optimized for the region $\mathcal R_1$ (panel b) and
                $\mathcal R_2$ (panel d). The dotted lines
                indicate the ODB and the dashed lines
                indicate the quasi-ODB.}
\end{figure}

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \label{Fig2}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $0.90$,
    corresponding to the quasi ODB of the
    structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Table \ref{tab:table2} shows the optimized values of the average
reflectance $\braket{R}$ for
different choices of the number of periods $p$ of each sub-mirror, as
discussed above, including the resulting number $N_m$ of stacked sub
mirrors, the thickness $d$ of the structure, and the optimal
overlap of consecutive PBGs. The first and second blocks correspond to
the first and second strategies discussed above.
\begin{table}[htbp]
        \centering
        \label{tab:table2}
        \begin{tabular}{rrrrr}
                $p$&$N_m$&$d (\mu\text{m})$&\% overlap&$\braket{R}$\\
                \hline
                \hline
                1&98&43.2&95&91.0\\
                3&31&42.5&81&91.8\\
                5&17&41.9&68&92.0\\
                \hline
                4&25&38.7&74&92.3\\
                \bf 6&\bf 18&\bf 41.5&\bf 78&\bf 95.4\\
                10&13&45.4&56&95.3\\
        \end{tabular}
        \caption{Total number $N_m$ of stacked sub-mirrors, thickness $d$,
                overlap between consecutive PBG and average reflectance
                $\braket{R}$ for optimized structures designed with a
                number $p$ of periods per sub-mirror (first block) or a number $p$
                of periods for those sub-mirrors tuned to wavelengths
                $\lambda_j\geq 800$ nm (second block, see text), for different
                values of $p$. The parameters corresponding to the best design
                are typeset in bold.}
\end{table}

According to table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
of 18 sub-mirrors tuned to the wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
        \begin{center}
                \includegraphics[width=\textwidth]
                {F3Alternativa.pdf}
        \end{center}
        \caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
                as a function of wavelength $\lambda$ and incidence angle
                $\theta$. (b) Measured and calculated reflectance spectra at several
                angles of incidence $\theta=10^\circ$, $20^\circ$,
                $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
                the region in which the reflectance is greater than $R>0.90$.  Inset shows a
                photograph with a top view of the synthesized structure.}
        \label{Fig3}
\end{figure}

@@

\begin{table}
        \centering
        \label{tab:table3}
        \begin{tabular}{rrrrr}
                Reference&Year&Sample&ODB (nm)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-    &1297-1615&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456 &506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&1321\\
                \hline
                &    &$S_1$&980-1340&360 \\
                This work                               &2021&$S_2$&980-2780&1800\\
                &    &$S_3$&950-2750&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
\end{table}

>>>>

\author[1]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

@@

\begin{table}
        \centering
        \addtolength{\tabcolsep}{-2pt}
        \begin{tabular}{rrrrrrrrrr}
                Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
                \hline
                \hline
                $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
                $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
                $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
                \hline
                $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
                $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
                $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
        \end{tabular}
        \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
                reflectance $\braket{R}$ averaged over the spectral ranges
                $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
                the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
                $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
                of the structure and the omnidirectional spectral
                width and center (ODW and ODC).}
        \label{tab:tableA}
\end{table}

The function $f_{3}$ yields after optimization the highest
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
structure. Furthermore, this
structure has an omnidirectional width (ODW) of 250 nm
centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
photonic structures have been reported with
ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
which $R>90\%$ for all angles. Here we we adopt the same criterium.
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
        \begin{center}
                \includegraphics[width=\textwidth]{F1Alternativa.pdf}
        \end{center}
        \caption{Profiles of the functions $f_n(\xi_j)$ optimized for
                the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
                $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
                for non-polarized light
                vs. wavelength and angle of incidence of the structure
                optimized for the region $\mathcal R_1$ (panel b) and
                $\mathcal R_2$ (panel d). The dotted lines
                indicate the ODB and the dashed lines
                indicate the quasi-ODB.}
        \label{Fig1}
\end{figure}

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $0.90$,
    corresponding to the quasi ODB of the
    structure. Inset: photograph of the synthesized structure.}
  \label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Table \ref{tab:table2} shows the optimized values of the average
reflectance $\braket{R}$ for
different choices of the number of periods $p$ of each sub-mirror, as
discussed above, including the resulting number $N_m$ of stacked sub
mirrors, the thickness $d$ of the structure, and the optimal
overlap of consecutive PBGs. The first and second blocks correspond to
the first and second strategies discussed above.
\begin{table}[htbp]
        \centering
        \begin{tabular}{rrrrr}
                $p$&$N_m$&$d (\mu\text{m})$&\% overlap&$\braket{R}$\\
                \hline
                \hline
                1&98&43.2&95&91.0\\
                3&31&42.5&81&91.8\\
                5&17&41.9&68&92.0\\
                \hline
                4&25&38.7&74&92.3\\
                \bf 6&\bf 18&\bf 41.5&\bf 78&\bf 95.4\\
                10&13&45.4&56&95.3\\
        \end{tabular}
        \caption{Total number $N_m$ of stacked sub-mirrors, thickness $d$,
                overlap between consecutive PBG and average reflectance
                $\braket{R}$ for optimized structures designed with a
                number $p$ of periods per sub-mirror (first block) or a number $p$
                of periods for those sub-mirrors tuned to wavelengths
                $\lambda_j\geq 800$ nm (second block, see text), for different
                values of $p$. The parameters corresponding to the best design
                are typeset in bold.}
        \label{tab:table2}
\end{table}

According to Table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
of 18 sub-mirrors tuned to the wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
        \begin{center}
                \includegraphics[width=\textwidth]
                {F3Alternativa.pdf}
        \end{center}
        \caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
                as a function of wavelength $\lambda$ and incidence angle
                $\theta$. (b) Measured and calculated reflectance spectra at several
                angles of incidence $\theta=10^\circ$, $20^\circ$,
                $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
                the region in which the reflectance is greater than $R>0.90$.  Inset shows a
                photograph with a top view of the synthesized structure.}
        \label{Fig3}
\end{figure}

@@

\begin{table}
        \centering
        \begin{tabular}{rrrrr}
                Reference&Year&Sample&ODB (nm)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-    &1297-1615&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456 &506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&1321\\
                \hline
                &    &$S_1$&980-1340&360 \\
                This work                               &2021&$S_2$&980-2780&1800\\
                &    &$S_3$&950-2750&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
        \label{tab:table3}
\end{table}
